---
output: github_document
---

# groupmissing

<!-- badges: start -->
<!-- badges: end -->

The `groupmissing` package provides a simple and effective way to count missing values in each column of a dataset, grouped by a specific factor.

## Installation

You can install the development version of `groupmissing` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("https://github.com/stat545ubc-2023/groupmissing")
```

## Examples

Here are basic examples which show you how to solve a common problem using 'count_all_missing_by_group' function in 'groupmissing' package:

```{r example}
library(groupmissing)
# Assuming 'data' is your data.frame and 'group' is the grouping variable: count_all_missing_by_group(data, group)
```

This example computes the number of missing values in the `airquality` dataset grouped by the `cyl` column. 

```{r}
count_all_missing_by_group(airquality, Month)
```

This example has the same output as the last example, but shows off an alternative way of invoking the `count_all_missing_by_group()`: piping the dataset into the function. 

```{r} 
airquality |> count_all_missing_by_group(Month) 
```

The optional `.groups` argument allows us to keep the output grouped by the grouping column. See example below; notice how the output is a grouped tibble, rather than the ungrouped tibble output of the earlier examples. 

```{r} 
count_all_missing_by_group(airquality, Month, .groups = "keep")
```

